Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
table changed

Second, the basic parameter determining if a tunnel will be detected is the bottleneck radius, i.e., the size of the narrowest part of the tunnel. 
This parameter is set to a specific value and even a slight decrease of the bottleneck radius below this threshold causes that the tunnel is not detected.
In consequence, the tunnels detected within an MD simulation are not continuous -- there are snapshots where the given tunnel is completely missing and may appear again after some time.
In fact this does not correspond to the real situation. 
The tunnel void space does not disappear completely in these snapshots, it only does not connect the active site with the protein surface by a sufficiently wide path.
To be able to trace the void space also in these snapshots, we introduce so called {\it dynamic tunnel}.
By this term we denote a void space between the protein active site and its surface, whose position and length is traced over time.
The dynamic tunnel does not need to be connected with the active site or the surface all the time.
By detecting these tunnel, the users gain more information about the void space also in snapshots without detected static tunnels.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. The number of frames
    with static tunnels, detected by CAVER 3.0.
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Dynamic tunnel}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}

>>>>

Second, the basic parameter determining if a tunnel will be detected is the bottleneck radius, i.e., the size of the narrowest part of the tunnel. 
This parameter is set to a specific value and even a slight decrease of the bottleneck radius below this threshold causes that the tunnel is not detected.
In consequence, the tunnels detected within an MD simulation are not continuous -- there are snapshots where the given tunnel is completely missing and may appear again after some time.
In fact this does not correspond to the real situation. 
The tunnel void space does not disappear completely in these snapshots, it only does not connect the active site with the protein surface by a sufficiently wide path.
To be able to trace the void space also in these snapshots, we introduce so called {\it dynamic tunnel}.
By this term we denote a void space between the protein active site and its surface, whose position and length is traced over time.
The dynamic tunnel does not need to be connected with the active site or the surface all the time.
By detecting these tunnels, the users gain more information about the void space also in snapshots without detected static tunnels.

@@

\begin{table}
\centering
\caption{\label{tab::dyn} The number of frames with detected dynamic tunnels. 
}
\begin{tabular}{ccccc}
\toprule
  \multirow{2}{*}{ Proposed algorithm}   &  \multicolumn{2}{c}{ Static tunnels}   \\
                                     &  {\bf Exists} & {\bf Not exists} \\
\midrule                                     
{\bf End of tunnel/cavity}           & 1,324/661 & 1,027/725  \\
{\bf Static tunnel}                  & 3,118     &  0   \\
{\bf No tunnel}                      & 669      & 1,833    \\ 
\bottomrule                                 
\end{tabular}
\end{table}
